### 2025-02-02 project2/nnMetamodels.tex
new
1

Deep neural networks (DNNs) have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has grown rapidly.
Two specialized neural network architectures that are relevant to our study are RNN~\citep{williams1989learning,sutskever2014sequence} and LSTM~\citep{hochreiter1997long,chung2014empirical}, as In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
Despite their success, DNN models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts are spent to test and improve the robustness of DNN models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for DNNs by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (CNN) can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of DNNs in financial and actuarial applications has been received by regulators with some skepticism.

The contributions of our study are two-fold:
\begin{enumerate}
    \item We study what DNNs learn from noisy data by training them using simulated data based on well-designed simulation experiments.
    This is a novel way to study the effect of noisy data and error tolerance of neural network models as one can \textit{reduce noise} in the data by increasing the number of replications in a simulation model.
    This new way of studying neural network models can provide more direct evidence on their transparency and interpretability. 
    \item We propose two generic nested simulation procedures that uses DNNs as metamodels to improve its efficiency while maintaining transparency. 
    In essence, a pilot stage simulation is used to generate a large number of noisy data, which are then used to train a metamodel.
    Depending on the application, a trained metamodel can serve two purposes: 
    \begin{itemize}
        \item to identify a set of tail scenarios, and 
        \item to estimate risk measures directly.
    \end{itemize}
    The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in stage 2, while the second procedure uses metamodel predictions to estimate risk measures directly.
    Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with similar accuracy while, at the same time, using less simulation budget.
\end{enumerate}

We are curious about fundamental questions like ``What do DNNs learn from noisy data?'' and ``How well do neural networks learn from noisy data?''.
Data-driven answers to these questions prevail in the existing literature.
In supervised learning, DNNs are believed to learn from the given data about the feature-label relationship to predict new labels for unseen features.
Cross-validation using to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
Generalization error on the test labels is another popular assessment metric.
However, the test set is also a subset of the original data.
In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
Instead of relying solely on real-data and splitting it into multiple subsets, we propose using stochastic simulation outputs as training labels for DNNs.
By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
In such a controlled environment, we obtain more clear-cut answers to the above fundamental questions.

In nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as the inner simulation model.
Borrowing terminologies from machine learning research, we can view a set of simulated outer scenarios and the estimated hedging errors for those scenarios as the \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
One can train supervised learning models using these simulated features and labels.
They are then used to replace the time-consuming inner simulations by the trained model.
We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use regression, kernel smoothing, and the likelihood ratio method, respectively.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical VA contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of DNN models in predicting the noiseless labels.
\end{enumerate}

In this chapter, DNN metamodels and DNN models are used almost interchangeably despite one distinction.
\begin{itemize}
    \item The discussion of \textit{DNN metamodels} focus more on the aspect of \textit{estimating} the inner simulation.
    \item Tthe discussion of \textit{DNN models} focus more on \textit{studying the DNN} using simulation data.
\end{itemize}

The rest of this chapter is organized as follows: 
Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce simulation budget by only performing computations on identified tail scenarios. 
Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
Practical suggestions are provided for the choice of suitable metamodels and simulation settings.

@@

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of VAs.
A main goal of the section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

\subsection{Tail Risk Measures: VaR and CVaR}
Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions like banks and insurance companies.
Two most popular tail risk measures are VaR and CVaR~\citep{hardy2022quantitative, rockafellar2002conditional}.

Consider a loss random variable $L$ whose losses and gains lie in the right and left tails, respectively, of its distribution.
For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR and $\alpha$-CVaR are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
Tail risk measures like VaR and CVaR are widely used for setting regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
For example, European insurers set regulatory capital at $99.5\%$-VaR according to Solvency II~\cite{eiopa2014underlying}.
In Canada, the regulatory capital requirement for VAs is set based on CVaRs as prescribed in~\cite{osfi2017life}.

Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the corresponding ordered losses.
For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$. Also, $\alpha$-CVaR can be estimated by
\begin{equation} \label{eq2:cvar-hat}
    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i}.
\end{equation}
Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
In this study, the loss random variable of interest is the hedging error for VA.

@@

VA contracts offer different types of guarantees.
Generally speaking, a portion of the VA premium is invested in a sub-account whose return is linked to some stock indices.

@@

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
The contract expires at $T'=\min\{T,\tau\}$, i.e., the earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be the indexed stock price, the subaccount value and the guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be the gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be the net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents the incurred investment expenses.

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in the following order:
\begin{enumerate}
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
        \begin{equation*}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
        \end{equation*} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.

    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value, i.e., 
        \begin{equation*}
            G_t = \max\{G_{t-1},F_t\}.
        \end{equation*}

    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value, i.e., 
        \begin{equation*}
            F_{t_+} = (F_t - I_t)^+,
        \end{equation*} 
    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
\end{enumerate}

We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ whose evolution is driven by the stochasticity of $S_t$.
In practice, the simulation model may also incorporate additional complications like mortality, lapse, and excess withdrawal, etc.

@@

For example, consider the time-$t$ liability $V_t$ of a GMWB:
Suppose that given the stock sample path, e.g., an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
\begin{align}\label{eq2:delta}
    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\} \cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1,
\end{align}
where $\bm{1}\{\cdot\}$ is an indicator function and
\begin{align*}
    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
\end{align*}
The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.85\textwidth]{./project2/figures/sns.pdf}
    \caption{Illustration of multi-period nested simulation that estimates the P\&L for one outer scenario.}
    \label{fig2:illustration}
\end{figure}

Insurers commonly use dynamic hedging to mitigate a market risk exposure in VA contract's embedded options.
In a dynamic hedging program, a hedge portfolio is set up and periodically rebalanced for a portfolio of VA contracts using stocks, bonds, futures, and other derivatives.
For simplicity, in this study we consider delta hedging for a generic VA liability using one stock and one bond.
The metamodeling procedures in Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage} can be trivially adapted to more general hedging strategies.

>>>>

Deep neural networks (DNNs) have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
Two specialized neural network architectures that are relevant to our study are RNN~\citep{williams1989learning,sutskever2014sequence} and LSTM~\citep{hochreiter1997long,chung2014empirical}.
In the field of actuarial science, a metamodel is commonly referred to as a proxy model.
Despite their success, DNN models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts have been spent to test and improve the robustness of DNN models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for DNNs by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (CNN) can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of DNNs in financial and actuarial applications has been received by regulators with some skepticism.

The contributions of our study in this chapter are two-fold:
\begin{enumerate}
    \item We study what DNNs learn from noisy data by training them using simulated data based on well-designed simulation experiments.
    This is a novel way to study the effect of noisy data and error tolerance of neural network models as one can \textit{reduce noise} in the data by increasing the number of replications in a simulation model.
    This new way of studying neural network models can provide more direct evidence on their transparency and interpretability. 
    \item We propose two generic nested simulation procedures that uses DNNs as metamodels to improve its efficiency while maintaining transparency. 
    In essence, a pilot stage simulation is used to generate a large number of noisy data, which are then used to train a metamodel.
    Depending on the application, a trained metamodel can serve two purposes: 
    \begin{itemize}
        \item to identify a set of tail scenarios, and 
        \item to estimate risk measures directly.
    \end{itemize}
    The first procedure uses a metamodel to identify a set of potential tail scenarios on which computations are performed in stage 2, while the second procedure uses metamodel predictions to estimate risk measures directly.
    Our numerical results show that DNN metamodels can identify the tail scenarios accurately and so the proposed procedures can estimate tail risk measures with a similar degree of accuracy while, at the same time, using less simulation budget.
\end{enumerate}

In essence, we are curious about two fundamental questions:
\begin{enumerate}
    \item ``What do DNNs learn from noisy data?'' and 
    \item ``How well do neural networks learn from noisy data?''.
\end{enumerate}
Data-driven answers to these questions prevail in the existing literature.
In supervised learning, DNNs are believed to learn from a given data about the feature-label relationship to predict new labels for unseen features.
A cross-validation procedure used to assess a subset, i.e., the validation set, of the original data, is a common way to access the quality of learning.
Generalization error on the test labels is another popular assessment metric.
However, the test set is also a subset of the original data.
In this study, we revisit these questions in a simulation context and propose an alternative approach to answer them.
Instead of relying solely on real-data and splitting it into multiple subsets, we propose using stochastic simulation outputs as training labels for DNNs.
By controlling the simulation design parameters, such as the number of independent replications, we can control the quality and also the quantity of the training labels fed into the neural networks.
In such a controlled environment, we obtain more clear-cut answers to the above fundamental questions.

In a nested simulation, a simulation model is used to generate a large number of outer scenarios, and each scenario is then used as an input to another simulation model, referred to as a inner simulation model.
Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
One can train supervised learning models using these simulated features and labels.
They are then used to replace the time-consuming inner simulations by the trained model.
We refer to the trained supervised learning models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using DNNs as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use DNNs as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the CVaR of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of variable annuity (VA) contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical VA contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of DNN models in predicting the noiseless labels.
\end{enumerate}

In this chapter, DNN metamodels and DNN models are used almost interchangeably despite one distinction.
\begin{itemize}
    \item The discussion of \textit{DNN metamodels} focuses more on the aspect of \textit{estimating} the inner simulation.
    \item The discussion of \textit{DNN models} focuses more on \textit{studying the DNN} using simulation data.
\end{itemize}

The rest of this chapter is organized as follows.
Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of VAs. 
Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses DNNs as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios. 
Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
Section~\ref{sec2:numerical} demonstrates the efficiency of DNN metamodels and examines the error tolerance of two LSTM metamodels with different numbers of trainable parameters. 
Lastly, practical suggestions are provided for the choice of suitable metamodels and simulation settings.

@@

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of VAs.
A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train DNN metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

\subsection{Tail Risk Measures: VaR and CVaR}
Measuring and monitoring risks, particularly tail risks, are important risk management tasks for financial institutions such as banks and insurance companies.
Two most popular tail risk measures are VaR and CVaR~\citep{hardy2022quantitative, rockafellar2002conditional}.

Consider a loss random variable $L$ which losses and gains lie in the right and left tails, respectively, of its distribution.
For a given confidence level $\alpha\in [0,1]$, the $\alpha$-VaR and $\alpha$-CVaR are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
Tail risk measures such as VaR and CVaR are widely used for setting a regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
For example, European insurers set regulatory capital at $99.5\%$-VaR according to Solvency II~\cite{eiopa2014underlying}.
In Canada, the regulatory capital requirement for VAs is set based on CVaRs as prescribed in~\cite{osfi2017life}.

Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the corresponding ordered losses.
For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$. Also, $\alpha$-CVaR can be estimated by
\begin{equation} \label{eq2:cvar-hat}
    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i}.
\end{equation}
Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except that we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
In this study, the loss random variable of interest is the hedging error for VA.

@@

VA contracts offer different types of guarantees.
Generally speaking, a portion of the VA premium is invested in a sub-account which return is linked to some stock indices.

@@

Consider a generic VA contract with maturity $T>0$ periods, e.g., $T=240$ months.
Denote the policyholder's (random) time of death by $\tau>0$.
The contract expires at $T'=\min\{T,\tau\}$, which isthe earlier of the contract maturity and the death of the policyholder.
Let $S_t$, $F_t$, and $G_t$ be an indexed stock price, the subaccount value and a guarantee value, respectively, at time $t=1,2,\ldots,T$.
Evolution of the subaccount value and the guarantee value of a VA contract affect the contract payout.
Note that the policyholder's (random) time of death also affects the timing of the benefit payout for certain types of VA such as GMDB, but this is not considered in our study for simplicity.
For clarity, we use $F_t$ and $F_{t_+}$ to denote the sub-account value just before and just after the withdrawal at time $t$, if any.
Let $\eta_g$ be a gross rate of management fee that is deducted from the fund value at each period and let $\eta_n < \eta_g$ be a net rate of management fee income to the insurer.
The difference between the gross management fee and the net management fee income represents incurred investment expenses.

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in order:
\begin{enumerate}
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted, which is, 
        \begin{equation*}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g),
        \end{equation*} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is a net management fee, i.e., $F_t\eta_n$.

    \item The guarantee value ratchets up (ratcheting is a common feature in GMWB) if the sub-account value exceeds the previous guarantee value,
        \begin{equation*}
            G_t = \max\{G_{t-1},F_t\}.
        \end{equation*}

    \item The withdrawal is made (for GMWB) and is deducted from the sub-account value,
        \begin{equation*}
            F_{t_+} = (F_t - I_t)^+,
        \end{equation*} 
    where $I_t = \gamma G_t$. A GMMB can be modeled with $\gamma = 0$.
\end{enumerate}

We see from the above modeling steps that the status of a generic VA contract is summarized by a triplet $(S_t,F_t,G_t)$ which evolution is driven by the stochasticity of $S_t$.
In practice, the simulation model may also incorporate additional complications such as mortality, lapse, and excess withdrawal, etc.

@@

For example, consider the time-$t$ liability $V_t$ of a GMWB:
Suppose that given the stock sample path, which is an outer path $S_1,\ldots,S_t$, one can simulate future stock prices $\Stilde_{t+1},\ldots,\Stilde_{T}$, e.g., inner sample paths, based on some asset model such as a Black-Scholes model.
The tilde symbol ($\sim$) over a quantity denotes its association with the inner simulation.
Given the time~$t$ state $(S_t,F_t,G_t)$, following~\cite{cathcart2015calculating} the sensitivity of $V_t$ with respect to $S_t$ can be estimated by a pathwise estimator~\citep{glasserman2004monte}:
\begin{align}\label{eq2:delta}
    \Delta_t(\Stilde_{t+1},\ldots,\Stilde_{T} | S_t) = \frac{\partial V_t}{\partial S_t} = \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_s > \Ftilde_s\} \cdot \left( \frac{\partial \Itilde_s}{ \partial S_t} - \frac{\partial \Ftilde_s}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_s}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1,
\end{align}
where $\bm{1}\{\cdot\}$ is an indicator function and
\begin{align*}
    \frac{\partial \Ftilde_s}{ \partial S_t} &= \bm{1}\{\Itilde_{s-1} < \Ftilde_{s-1}\}\cdot\left( \frac{\partial \Ftilde_{s-1}}{ \partial S_t} - \frac{\partial \Itilde_{s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_s}{\Stilde_{s-1}}\cdot (1-\eta_g),\\
    \frac{\partial \Gtilde_s}{ \partial S_t} &= \bm{1}\{\Gtilde_{s-1} < \Ftilde_{s}\}\cdot\frac{\partial \Ftilde_{s}}{ \partial S_t} + \bm{1}\{\Gtilde_{s-1} \geq \Ftilde_{s}\}\cdot\frac{\partial \Gtilde_{s-1}}{ \partial S_t},\\
    \frac{\partial \Itilde_s}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_s}{ \partial S_t}.
\end{align*}
The recursion is initialized with $(\Stilde_t,\Ftilde_t,\Gtilde_t) = (S_t,F_t,G_t)$, $\frac{\partial \Ftilde_s}{ \partial S_t} = \frac{\Ftilde_t}{S_t}$, and $\frac{\partial \Gtilde_s}{ \partial S_t} = \frac{\partial \Itilde_s}{ \partial S_t} = 0$.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.85\textwidth]{./project2/figures/sns.pdf}
    \caption{Illustration of a multi-period nested simulation that estimates the P\&L for one outer scenario.}
    \label{fig2:illustration}
\end{figure}

Insurers commonly use dynamic hedging to mitigate a market risk exposure in VA contract's embedded options.
In a dynamic hedging program, a hedge portfolio is set up and periodically rebalanced for a portfolio of VA contracts using stocks, bonds, futures, and other derivatives.
For simplicity, in this study we consider delta hedging for a generic VA liability using one stock and one bond.
The metamodeling procedures presented in Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage} can be trivially adapted to more general hedging strategies.

Consider a VA contract which delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is an underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
\end{equation*}
Therefore, the time~$t$ hedging error, which is the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}\label{eq2:hedgingerror}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The P\&L of the VA contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
Mathematically, the present value of these cash flows is given by
\begin{equation}\label{eq2:lossrv}
L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
\end{equation}
where the second equality holds by a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.
